Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 response.md

Finally, we have modified Equation 2 to match the normalization of Equation 4 (as suggested in minor comment 4).

-----------------------------------
Minor Comment 1
-----------------------------------

***1) Section 3.2: what checking did the authors do to indicate that giving all anonymous classifications a weight of 1 is valid?***

From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown). However, there are large amounts of data from similar projects that support this approach. For the Galaxy Zoo: CANDELS project (Simmons et al. 2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7). The anonymous users have slightly broader wings, with slightly more addresses at the lowest and highest levels of consistency, but the overall behavior is similar.

The roughly 50-50 split between logged-in users and non-logged-in IP addresses is typical of the ratio for Zooniverse crowdsourced projects as a group. Similar results have been published for the Planet Hunters project (Schwamb et al. 2012) and have been seen in unpublished data for Pulsar Hunters (https://www.zooniverse.org/projects/zooniverse/pulsar-hunters).

@@

Use of a different method such as a tree could potentially prove to be a superior separator. However, the new normalization technique used in this draft results in very clean separation based on the convex hull, with only a single adjustment (see https://github.com/willettk/gzhubble/blob/master/python/creating_debiased_catalog/STEP_3_ferengi_smooth_function.ipynb). Further optimization would have an extremely minimal effect on the overall results.

----------------------------------
Minor Comment 8
----------------------------------

***8) Section 4.2: "In each unclassifiable (shaded blue) z,mu bin, the spread of intrinsic values for f_features,z=0.3 for four ranges of observed f_features is computed." Where did the "four" come from? More explanation needed.***

We chose to evaluate the distribution of f_features in 5 (not 4; a typo in the earlier manuscript has been corrected) bins to match some of the common ranges of vote fractions used in previous GZ morphological studies. The bin size is chosen to be roughly twice the size of the typical scatter for any individual galaxy (which has been measured using repeat image classifications in several phases of Galaxy Zoo), and so any finer grained intervals will begin to simply fit the noise.

Some clarification has been added to the text at the end of Section 4.1.

@@

----------------------------------
Minor Comment 9
----------------------------------

***9) Why 80% of the data (orange bars, Figure 10)? This is an ad hoc choice that doesn't correspond to any typical statistical practice (except perhaps a 10% trimmed mean, but the authors are not computing means here). And how is this information applied in Figure 11, middle panel? This is not clear.***

The authors agree with the referee that a more typical statistical range would be appropriate. We have changed the range to upper and lower 1 sigma limits, or the inner 68% of the data. The figure (now Figure 8) has been modified and text added to the end of Section 4.1.

### 2016-09-07 response.md

We used the referee's input to review and revise the fitting of the artificially-redshifted images (from FERENGI) and construction of the debiasing equation for the Hubble data, as follows:

We tested a variety of models for fitting f/f_0, including linear, quadratic, cubic, and exponential dependences on redshift; for each of these functional forms, we also tested combinations using either a constant zeta parameter or a zeta function that linearly depends on surface brightness. We compared the relative quality of fits using the Akaike information criteria (AIC); for each case, we found no significant differences in the results based on the choice of model. Full details and code for these tests can be viewed in this Python notebook: https://github.com/willettk/gzhubble/blob/master/python/notebooks/zeta_models_compared.ipynb.

Of all the models tested, we believe the best model is an exponential fit for f_features vs redshift using a linear dependence on zeta. This decision is based on the following points:

1) While the FERENGI data can be fit relatively well using any of the above models, the exponential is ideal because it is the only form whose limiting behaviour can be set to approach 0 and 1. This is a key requirement for the debiased votes so that they can be interpreted as normalized fractions. Furthermore, the results of the AIC test show that the exponential fit is either better than, or had similar support to the other models tested.

### 2016-09-08 response.md

We thank the referee for the very thorough analysis and for the detailed suggestions that helped to improve the analysis and the paper overall. In the following, we provide the original comment by the referee, followed by our response. 
In the manuscript, we highlighted our changes in boldface.

@@

Finally, we have modified Equation 2 to match the normalization of Equation 4 (as suggested in minor comment 4).

-----------------------------------
Minor Comment 1
-----------------------------------

***1) Section 3.2: what checking did the authors do to indicate that giving all anonymous classifications a weight of 1 is valid?***

From a strict sense, it is impossible to tell a priori if giving the anonymous classifiers a weight of 1 is valid (since the grouping within the anonymous data is unknown). However, there are large amounts of data from similar projects that support this approach. For the Galaxy Zoo: CANDELS project (Simmons et al. 2016, submitted), which is nearly identical in design to Galaxy Zoo: Hubble and shares a large fraction of the same user base, the distribution of the classifier consistency for both the logged-in and non-logged-in populations peak at the same value (kappa = 0.7). The anonymous users have slightly broader wings, with slightly more IP addresses at the lowest and highest levels of consistency, but the overall behavior is similar.

### 2016-09-08 writeup/gz_hubble_data.tex
Most major and minor changes added back to primary manuscript.

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $w$ was 1 for the top 95\% of classifiers, as ranked by consistency.
For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
effectively zero for the bottom 1\% in the distribution function. Since
downweighting only occurs for the bottom few percent of classifiers (and an even smaller
percentage of the classifications), the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority
of logged-in classifiers.
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated using a method visualised in Figure~\ref{fig:f_vs_f_zoom}. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
we compute the spread of
intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
(corresponding to the ``clean'' thresholds used in prior GZ publications).
The range of intrinsic values for GZH is defined as the inner 80\% of the data,
represented by the orange bars in Figure~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the
best-fit model for a random set of galaxies in the \ferengi{} sample. The
results show that there is a clear dependence on redshift for the observed
changes in \ffeatures. To examine whether a better fit should involve
additional parameters, we examine the global dependence of $\zeta$ on the
galaxy surface brightness. This is motivated by the fact that brighter galaxies
would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
changes in \ffeatures{} depend on a combination of physical size and
absolute magnitude. To simplify our model, we subsume these into a single
parameter $\mu$.

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
(from least-squares optimization) are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
final debiased correction, we use Equation~\ref{eqn:fzeta}, rearranged for clarity:

@@

\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
described in Section~\ref{ssec:weighting}, and here $f_{\rm features,debiased}$ is bounded 
between $f_{\rm features,weighted}$ and 1.

Few galaxies in the sample have sufficiently high corrections to completely
change them from being confidently ``smooth'' to ``featured'' following the
correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
check, we compare morphologies of highly boosted galaxies to the expert visual
classifications in CANDELS \citep{kar15}.  Only nine galaxies that
were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
appear in the CANDELS expert sample. Of those, \citet{kar15}
classify 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
between 0.5 and 0.7, making them all intermediate disk candidates. Visual
inspection of the GZH images shows extended disk structure in at least
5~images; the remaining 4 are either extremely faint or have imaging artifacts
in the ACS data.  Since the surveys use different rest-frame filters and the
overlap sample is tiny, though, detailed comparisons between the overall
morphologies are highly difficult (see
Sections~\ref{ssec:comparisons}--\ref{ssec:gzh_gzc}).

@@

In the \ferengi{} data, these numbers severely limit the amount of information
that can be extracted for the higher-tier questions. The debiasing technique
used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
image at higher redshift. This requirement is (by default) met by all galaxies
for the smooth/features question. However, this is often \emph{not} met for
questions beyond Task~01. On average, $60\%\pm24\%$ of the galaxies do not have
sufficient data to measure a correction, as compared to 2.0\% achieved for
Task~01 (Table~\ref{tbl:ferengi_corrections}). Of the remaining
\ferengi{} galaxies which did meet this requirement, polynomials were fit to
the data in each redshift-surface brightness bin, as was done for Task~01. The
goodness-of-fit was evaluated in each bin, for each Task, using a normalised
$\chi^2$ metric. The mean $\chi^2$ for all higher-order tasks was
$0.10\pm0.04$, significantly larger than the Task~01 value of $0.04$. Based on
this statistic, the data cannot not be modelled with sufficient confidence for
the higher order tasks. An example of the debiasing technique applied to
\fbar{} is shown in Section~\ref{sec:ferengi_bar}; visual inspection of
Figure~\ref{fig:f_vs_fbar} confirms that the points in each bin are scattered
to a degree at which no strong correlation is present.  For these reasons,
debiased vote fractions are only offered in the GZH catalogue for Task~01
(smooth/features).

@@

Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn} also contain flags for
Task 01 that identify clean (but not complete) samples of galaxies with high
likelihoods of being either smooth, featured, or a star/artifact.  These are
set as $\tt smooth/featured/artifact\_flag=1$ if $\rm
f_{smooth/features/artifact\_best}>0.8$. For a galaxy to be flagged as
``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is
applied. This accounts for the uncertainty in distinguishing between genuine
ellipticals and disks whose features have been washed out due to surface
brightness and redshift effects (Section~\ref{sec:debiasing}).

Data products for GZH are split by the type of image being classified. Each
sample in Section~\ref{ssec:sample_labels} corresponds to the data in
Tables~\ref{tbl:catalogue_hst}-\ref{tbl:simulated_agn}.

@@

\section{Using the catalogue}\label{sec:cookbook}

@@

As an example of how to use Table~\ref{tbl:thresholds} to create a sample of
3-armed spiral galaxies, we suggest selecting objects with $N_{arm~number} \ge
20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and
$f_{spiral,yes}>0.25$. These cuts define a sample of galaxies of ``arm number
candidates''; \ie, galaxies for which answering the arm number question makes
physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. In
this example, such galaxies are featured, non-clumpy, non-edge~on spirals. At
this point a cut can be made on $f_{\rm arm~number=3}$ to select spirals with
three arms.

@@

As an example of visualising the overall morphological distribution,
Figure~\ref{fig:sankey} shows the breakdown of GZH morphologies as a flow
diagram. In order to show a physically meaningful sample,
Figure~\ref{fig:sankey} only includes images from a volume-limited sample
($z<1.0, m_\mathrm{I}<22.5$) in a single \hst{} survey (COSMOS, which has the
largest number of total galaxies).  We use a simple plurality vote for the
responses to each task to characterise the morphologies.  This emphasises one
of the basic results of the GZH project; namely, that there are comparable
numbers of spheroid and disk galaxies in the Universe at $z\sim1$, with
significant diversity in the arrangement of spiral arms and internal clumps.

\begin{figure*}
\center
\includegraphics[width=0.90\textwidth]{figures/sankey_cosmos.pdf}
\caption{Demographics of the morphologies for GZH from a volume-limited
sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies. Each node in the diagram (dark blue horizontal
bars of uniform height) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
the full decision tree. The right diagram zooms in on the features/clumpy
tasks, which are otherwise difficult to see. Paths between tasks represent
each possible answer to the task, flowing from top to bottom between their
origin and the subsequent task in the tree. Labels are assigned to
each galaxy based on the plurality answer for each task. A galaxy is assigned
only one label at each node. Widths of the paths are proportional to the number
of galaxies assigned to that path. The widths of the nodes are proportional to
the number of galaxies for which the question was reliably answered.}
\label{fig:sankey}
\end{figure*}

@@

There are 7,681~galaxies in the GOODS-S field with morphological
classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
et~al., submitted). Since both the sensitivity and filters for the two sets of
images are significantly different (and there is no correction for redshift
bias applied to GZC), there is no prior reason to expect a perfect correlation
between the separate vote fractions for the projects. Briefly, we note that the
\ffeatures{} value for GZH is on average higher than GZC; the effect is
strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies
have $f_\mathrm{features,GZH}>0.5$. However, the correlation between vote
fractions is single-valued (although not linear, with a Pearson correlation
coefficient of $r=0.6$), and should be possible to calibrate using a similar
approach to that described in Section~\ref{sec:debiasing}; the correlation
between other tasks, such as edge-on galaxies is significantly stronger
($r=0.9$). So while the raw vote fractions are not directly comparable, the
initial analysis indicates that the broad morphologies are at least consistent.

@@

All of the Legacy surveys included in the GZH imaging have had morphological
catalogues previously published; these have significant differences in
the number of galaxies, size and magnitude limits, classification scheme, and
the methods used for measuring morphology. These catalogues have been
cross-matched to GZH to compare the results. 
%This is not presented as an
%endorsement of any particular method, but as an exploration of the strengths
%and weaknesses of the Galaxy~Zoo crowdsourced catalogues compared to products
%made with machine learning, automatic fits, and expert visual classification.

The types and accuracy of morphological classification strongly depend on the
sample and methods being used. In an attempt to make a consistent comparison
between different techniques, galaxies are broadly grouped into three
categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
irregular/clumpy. These categories are compared to two parameters in GZH:
\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd, which
identifies deviations from well-formed spirals or S0s and which constitutes a
``catch-all'' for the variety of asymmetric morphologies that can constitute an
irregular galaxy.

@@

COSMOS galaxies have multiple published datasets automatically classifying
morphology, all using a variation of non-parametric measurements. \citet{cas07}
used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
\citep{cas05} make empirical divisions based on several hundred training images
to assign galaxy morphology. A similar method was employed by \citet{tas11},
using the same non-parametric indices but with a different method of
calculating the Petrosian radius and total light profile, and using a
nearest-neighbors method to label morphologies. \citet[][ZEST]{sca07} used $C$,
$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
($n$) to quantify morphology; a principal component analysis is used to assign
galaxies to categories. All three methods use discrete morphological categories
of ellipticals, spirals, and peculiar/irregulars. We use the same categories
with the exception of assigning S0/bulge-dominated disks (type~2.0) from ZEST
into the unfeatured category.

Galaxies from the COSMOS morphology catalogues all have morphologies that are
reasonably well-predicted by the GZH based on \fbest. The relation is strongest
for early-type galaxies, since the comparable fractions of irregulars and
spirals shows that clumpy/asymmetric morphologies are clearly also being
captured by the \fbest{} parameter. The small dropoff in the fraction of
early-types for the Cassata and ZEST samples at \fbest$<0.1$ in
Figure~\ref{fig:comparisons_features} is somewhat puzzling, but could
potentially be due to the presence of a small population of extremely
compact objects (stars or quasars) that would be classified as artifacts in
GZH, explaining the dip in \fbest.

A detailed comparison of all external catalogues is outside the scope of this
paper, but we emphasise only that it is impossible for any catalogue to be fully
consistent with all of the previously published datasets (for example, only
64\% of the galaxies in \citealt{tas11} have the same morphological class as
the same galaxies in \citealt{cas07}). We interpret the broad agreements
between early-types, spirals, and irregulars between GZH and all three methods
of automated classification as a validation of both the crowdsourced visual
classifications provided by GZH and those automated methods.

It has been argued that automated methods are preferable to visual
classification due to being quantified and more easily reproducible
\citep[\eg,][]{con14,paw16}. We argue that this distinction applies only to
visual classification done by individual and/or small numbers of experts. The
technique of crowdsourcing using a large number of independent classifiers
provides visual classification which is both quantified, and reproducible, and
(as demonstrated in this section), broadly agrees with all the automated
methods and expert visual classifications.

We repeated all analyses comparing morphologies between GZH and external
pulblications on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.

@@

The data for the GZH catalogues has been extensively tested and reduced. The
dominant effect is a known bias against identifying disky and asymmetric
sub-structures at either low resolution or surface brightness. This can be the
result either of genuinely small or dim galaxies, or a perceived effect from
observing galaxies at further distances (higher redshift). To calibrate this
\emph{without} potentially overcorrecting for the genuine morphological
evolution of galaxies over cosmic time, the GZH project uses SDSS images of
low-redshift galaxies, processes them to appear as if they were at higher
redshift, and classifies them through the GZH interface in an identical
fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
applied as a multiplicative correction to the top-level vote fractions for
$\sim50\%$ of the GZH galaxies.

>>>>

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $w$ was 1 for the top 95\% of classifiers as ranked by consistency.
For the bottom 5\% of classifiers, $w$ drops smoothly and is
effectively zero for the bottom 1\% of the distribution function. Since
downweighting only occurs for the bottom few percent of classifiers (and an even smaller
percentage of the classifications), the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.

Classifications for GZH were weighted only if the classifier was logged
into the site under their username (this was encouraged, but not required for
participation). Classifications by participants who were not logged in were marked as
``Anonymous'' and receive the same $w=1$ weighting as the vast majority of
logged-in classifiers. \changes{Results from the Galaxy Zoo: CANDELS project (Simmons et~al., submitted)
show that the distributions of weights for anonymous and
logged-in users are similar, supporting the default technique of GZH.}
% We should also try to estimate how many anonymous classifiers there were, if possible. 
% Not clear that I can do that given the SQL data

@@

For the ``lower-limit'' galaxies for which a single debiased \ffeatures{} value
cannot be confidently assigned, the \emph{range} of debiased values is
estimated and included as a data product. This uses the
\ferengi{} simulated data to analyse the range of intrinsic \ffeaturesrest{}
values for any given observed \ffeatures{} value, again as a function of
surface brightness and redshift. \changes{In each unclassifiable (shaded blue) $z$,$\mu$ bin, 
we compute the spread of
intrinsic values of \ffeaturesrest{} for five quantiles of observed \ffeatures{}
(corresponding to the ``clean'' thresholds used in prior GZ publications).
The range of intrinsic values for GZH is defined by the upper and lower 1~$\sigma$ limits,
enclosing the inner 68\% of the data. This range is represented by the orange bars in 
Figure}~\ref{fig:f_vs_f_zoom}. For any galaxy which
cannot be directly debiased by the $\zeta$ method, these ranges are used to
denote the upper and lower limits on the expected values \ffeaturesrest{} as a
function of the observed \ffeatures.

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{]Behaviour of the normalised, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}

Figure~\ref{fig:zeta_examples} shows the change in vote fraction and the
best-fit model for a random set of galaxies in the \ferengi{} sample. The
results show that there is a clear dependence on redshift for the observed
changes in \ffeatures. To examine whether a better fit should involve
additional parameters, we tested the global dependence of $\zeta$ on the
galaxy surface brightness. This is motivated by the fact that brighter galaxies
would presumably be easier to identify; \citet{bam09} and \citet{wil13} found
changes in \ffeatures{} depend on a combination of physical size and
absolute magnitude. To simplify our model, we subsume these into a single
parameter of surface brightness, $\mu$.

@@

\noindent where $\hat\zeta$ is the correction factor applied to each galaxy as
a function of surface brightness. The best-fit parameters to the linear fit
from least-squares optimization are $\zeta_0=0.50$, $\zeta_1=-0.03$. To make the
final debiased correction \changes{for the genuine \hst{} data, we apply a 
correction similar to Equation~\ref{eqn:fzeta}:}

@@

\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
described in Section~\ref{ssec:weighting}, and $f_{\rm features,debiased}$ is bounded 
between $f_{\rm features,weighted}$ and 1.

Few galaxies in the sample have sufficiently high corrections to completely
change them from being confidently ``smooth'' to ``featured'' following the
correction for redshift bias (Figure~\ref{fig:debiased_corrections}). As a
check, we compare morphologies of highly boosted galaxies to the expert visual
classifications in CANDELS \citep{kar15}.  Only nine galaxies that
were strongly boosted (\ffeatures$<0.25$ and \fbest$>0.50$) in GZH also
appear in the CANDELS expert sample. Of those, the CANDELS expert sample
classifies 4 as spheroids/disky, 2 as disks, 1 as a spheroid, 1 as
irregular/disky and 1 as unclassifiable. The \fbest{} values for GZH are all
between 0.5 and 0.7, making them all intermediate disk candidates. Visual
inspection of the GZH images shows extended disk structure in at least
5~images; the remaining 4 are either extremely faint or have imaging artifacts
in the ACS data.  Since the surveys use different rest-frame filters and the
overlap sample is tiny, though, detailed comparisons between the overall
morphologies are highly difficult (see
Sections~\ref{ssec:gzh_gzc}--\ref{ssec:comparisons}).

@@

In the \ferengi{} data, these numbers severely limit the amount of information
that can be extracted for the higher-tier questions. The debiasing technique
used (Section~\ref{ssec:zeta}) requires that at least 10~classifiers answer each
question for a galaxy with $z_\mathrm{sim}=0.3$ \emph{and} the corresponding
image at higher redshift. This requirement is (by default) met by all galaxies
for the smooth/features question. However, this is often \emph{not} met for
questions beyond Task~01. On average, $60\%\pm24\%$ of the galaxies do not have
sufficient data to measure a correction, as compared to 2.0\% achieved for
Task~01 (Table~\ref{tbl:ferengi_corrections}). \changes{This leaves the average
surface brightness/redshift bin 
with insufficient data points to confidently measure the change in vote fraction ($\lesssim10$~galaxies per bin). 
For these reasons, debiased vote fractions are only provided in the GZH catalogue for Task~01
(smooth/features). We suggest that use of morphological data for higher order tasks should instead use
the weighted vote fractions (see Section~\ref{sec:cookbook}).}

@@

Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn} also contain flags for
Task 01 that identify clean (but not complete) samples of galaxies with high
likelihoods of being either smooth, featured, or a star/artifact.  These are
set as $\tt smooth/featured/artifact\_flag=1$ if $\rm
f_{smooth/features/artifact\_best}>0.8$. For a galaxy to be flagged as
``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is
applied. This accounts for the uncertainty in distinguishing between genuine
ellipticals and disks whose features have been washed out due to surface
brightness and redshift effects (Section~\ref{sec:debiasing}).

Data products for GZH are split by the type of image being classified. Each
sample in Section~\ref{ssec:sample_labels} corresponds to the data in
Tables~\ref{tbl:catalog_hst}-\ref{tbl:simulated_agn}.

@@

\section{Using the GZH catalogue}\label{sec:cookbook}

@@

To use data from Table~\ref{tbl:thresholds} to create, for example, a sample of  
3-armed spiral galaxies, we suggest selecting objects with $N_{arm~number} \ge
20$, \ffeatures$>0.23, f_{\rm clumpy,no} > 0.30, f_{edgeon,no}>0.25$, and
$f_{spiral,yes}>0.25$. These cuts define a sample of galaxies of ``arm number
candidates''; \ie, galaxies for which answering the arm number question makes
physical sense and the vote fraction $f_{\rm arm~number}$ is well-sampled. 
Such galaxies will be featured, non-clumpy, non-edge~on spirals. At
this point a final cut can be made on $f_{\rm arm~number=3}$ to select spirals with
three arms.

@@

As an example of visualising the overall morphological distribution,
Figure~\ref{fig:sankey} shows the breakdown of GZH morphologies as a flow
diagram. In order to show a physically meaningful sample,
Figure~\ref{fig:sankey} only includes images from a volume-limited sample
($z<1.0, m<22.5$ in $I$-band) in a single \hst{} survey (COSMOS, which has the
largest number of total galaxies).  We use a simple plurality vote for the
responses to each task to characterise the morphologies.  This emphasises one
of the basic results of the GZH project; namely, that there are comparable
numbers of spheroid and disk galaxies in the Universe at $z\sim1$, with
significant diversity in the arrangement of spiral arms and internal clumps.

\begin{figure*}
\center
\includegraphics[width=0.90\textwidth]{figures/sankey_cosmos.pdf}
\caption{Demographics of the morphologies for a volume-limited
sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies in GZH. Each node in the diagram (dark blue horizontal
bars) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
the full decision tree. The right diagram zooms in on the features/clumpy
tasks only. Paths between tasks represent
each possible answer to the task, flowing from top to bottom between their
origin and the subsequent task in the tree. Labels are assigned to
galaxies based on the plurality answer for each task, with each galaxy assigned
only one label per node. Widths of the paths are proportional to the number
of galaxies assigned to that path. The widths of the nodes are proportional to
the number of galaxies for which the question was reliably answered.}
\label{fig:sankey}
\end{figure*}

@@

There are 7,681~galaxies in the GOODS-S field with morphological
classifications in both GZH and the Galaxy~Zoo:~CANDELS project (Simmons
et~al., submitted). Since both the sensitivity and filters for the two sets of
images are significantly different (and there is no correction for redshift
bias applied to GZC), there is no prior reason to expect a perfect correlation
between the separate vote fractions for the projects. Briefly, we note that the
\ffeatures{} value for GZH is on average higher than GZC; the effect is
strongest at $f_\mathrm{features,GZC}<0.3$, for which roughly half the galaxies
have $f_\mathrm{features,GZH}>0.5$. However, the correlation between vote
fractions is single-valued (although not linear, with a Pearson correlation
coefficient of $r=0.6$), and should be possible to calibrate using a similar
approach to that described in Section~\ref{sec:debiasing}; the correlation
between other tasks, such as edge-on galaxies, is significantly stronger
($r=0.9$). While the raw vote fractions are not directly comparable, the
initial analysis indicates that the broad morphologies are at least consistent.

@@

All of the Legacy surveys included in the GZH imaging have had morphological
catalogues previously published; these have significant differences in
the number of galaxies, size and magnitude limits, classification scheme, and
the methods used for measuring morphology. These catalogues have been
cross-matched to GZH to compare results. 
%This is not presented as an
%endorsement of any particular method, but as an exploration of the strengths
%and weaknesses of the Galaxy~Zoo crowdsourced catalogues compared to products
%made with machine learning, automatic fits, and expert visual classification.

The types and accuracy of morphological classification strongly depend on the
sample and methods being used. In an attempt to make a consistent comparison
between different techniques, galaxies are broadly grouped into three
categories: bulge-dominated/elliptical/smooth, disk-dominated/spiral, and
irregular/clumpy. These categories are matched to two GZH parameters:
\fbest, which identifies disk-dominated and clumpy galaxies, and \fodd, which
identifies deviations from well-formed spirals or S0s and which constitutes a
``catch-all'' for the variety of asymmetric morphologies that can constitute an
irregular galaxy.

@@

COSMOS galaxies have multiple published datasets automatically classifying
morphology, all using a variation of non-parametric measurements. \citet{cas07}
used a combination of concentration ($C$), asymmetry ($A$), $G$, and $M_{20}$
\citep{cas05} make empirical divisions based on several hundred training images
to assign galaxy morphology. A similar method was employed by \citet{tas11},
using the same non-parametric indices but with a different method of
calculating the Petrosian radius and total light profile, and using a
nearest-neighbors method to label morphologies. \citet[][ZEST]{sca07} used $C$,
$A$, $G$, $M_{20}$, the galaxy ellipticity ($\epsilon$), and \sersic{} index
($n$) to quantify morphology; a principal component analysis is used to assign
galaxies to categories. All three COSMOS catalogs use discrete morphological categories
of ellipticals, spirals, and peculiar/irregulars. We use the same categories
with the exception of assigning S0/bulge-dominated disks (type~2.0) from ZEST
into the unfeatured category.

Galaxies from the COSMOS catalogues all have morphologies that are
reasonably well-predicted by the GZH based on \fbest. The relation is strongest
for early-type galaxies, since the comparable fractions of irregulars and
spirals shows that clumpy/asymmetric morphologies are clearly also being
captured by the \fbest{} parameter. The small dropoff in the fraction of
early-types for the Cassata and ZEST samples at \fbest$<0.1$ in
Figure~\ref{fig:comparisons_features} is somewhat puzzling, but could
potentially be due to the presence of a small population of extremely
compact objects (stars or quasars) that would be classified as artifacts in
GZH.

A detailed comparison of all external catalogues is outside the scope of this
paper, but we emphasise only that it is impossible for any catalogue to be fully
consistent with \emph{all} of the previously published datasets (for example, only
64\% of the galaxies in \citealt{tas11} have the same morphological class as
the same galaxies in \citealt{cas07}). We interpret the broad agreements
between early-types, spirals, and irregulars between GZH and all three methods
of automated classification as a validation of both the crowdsourced visual
classifications provided by GZH and those automated methods.

It has been proposed that automated methods are preferable to visual
classification due to being quantified and more easily reproducible
\citep[\eg,][]{con14,paw16}. We argue that this distinction applies only to
visual classification done by individual and/or small numbers of experts. The
technique of crowdsourcing using a large number of independent classifiers
provides visual classification which is both quantified, and reproducible, and
(as demonstrated in this section), broadly agrees with all the automated
methods and expert visual classifications.

We repeated all analyses comparing morphologies between GZH and external
\changes{publications} on the entire GZH dataset, rather than the volume-limited sample
($z<1.0,m<22.5$) discussed above. If galaxies at all redshifts and at the
original magnitude limit of $m<23.5$ are used, the correlations between all of
the automatic morphological populations and GZH decrease significantly.  The
exceptions are the GEMS galaxies, which are the only sample that was visually
classified and had a shallower magnitude cut on their catalogue.  Based on
these comparisons, we suggest that use of morphological catalogues with these
\hst{} images be limited to galaxies with $m_\mathrm{I|i|z}<22.5$; fainter
targets have been demonstrated to be less reliable, regardless of the method of
morphological classification being used.

@@

The data in the GZH catalogues have been extensively reduced and tested. A
dominant effect is the known bias against identifying disky and asymmetric
sub-structures at either low resolution or surface brightness. This can be the
result either of genuinely small or dim galaxies, or a perceived effect from
observing galaxies at further distances (higher redshift). To calibrate this
\emph{without} potentially overcorrecting for the genuine morphological
evolution of galaxies over cosmic time, the GZH project uses SDSS images of
low-redshift galaxies, processes them to appear as if they were at higher
redshift, and classifies them through the GZH interface in an identical
fashion. The resulting change in \ffeatures{} as a function of $z$ and $\mu$ is
applied as a multiplicative correction to the top-level vote fractions for
$\sim50\%$ of the GZH galaxies.
